Supplementary Information

### 2020-08-28 doc/manuscript/MEE_manuscript_SI.Rmd
small update

\newpage 
## Figure S1. Comparison of our approach with traditional methods of identifying climate signals
![**Figure S1 | (Comparison of traditional approaches with ours).**  (THIS FIGURE IS JUST A MOCK-UP TO SHOW VALENTINE WHAT I HAVE IN MIND.) ](tables_figures/mock_comparison_traditional_method.png){ width=70% }

>>>>

\newpage 
## Figure S1. Comparison of our approach with traditional methods of identifying climate signals
![**Figure S1 | (Comparison of traditional approaches with ours).**  (THIS FIGURE IS JUST A MOCK-UP --NOT REAL DATA. REAL FIGURE WILL INCLUDE 3-4 COMMONLY STUDIED SPECIES FROM DIFFERENT SITES.) ](tables_figures/mock_comparison_traditional_method.png){ width=70% }
